Regression Cube Analysis of Cohort Study Data

### 2015-03-29 draft.tex
merged with Sylvias revision

%% INTERACTION
Rotating with the cube is restricted to the y-axis, preserving the mental map to position individual features.
%%
The cube is always oriented according to the 2D-representation, allowing for an easy mental combination of the two representations.
%%
Allowing more degrees of freedom was confusing to our users and also did not add value to the visualization.
%%
We provide also a zoom functionality using the mouse wheel input.
%%
%\\\\
\paragraph{Cube Slice Selection [3.ZF].}
%%
In order to \emph{Zoom, Filter and Analyze Further}, the user has to navigate towards different slices of interest.
%%
We propose two ways to achieve this.
\begin{itemize}
	\item \emph{Applying the slicing metaphor from 3D volume data.}
	%%
	In medical volume data renderings, slicing views very common to view details on a selected plane in the scene.
	%%
	We employ this technique for selecting cube slices (e.g. by moving a plane via vertical mouse input while pressing the right mouse button).
	%%
	We, however, still display the whole 3D-object instead of cutting away information towards the slice position.
	%%
	\item \emph{Selecting the slice using a dropdown menu} provides fast access to plane selections when the user already knows the slices of interest.
	%%
\end{itemize}
%%
The currently selected slice is denoted with a semi-transparent gray plane.
%%
The space available from visualizing only the prism generated from the upper half of the cube diagonal is used to display information about the current selected plane.
%%
the values are projected on this plane to give an overlapping-free view on the data points, which makes it easier to identify the current slice.
%%
%It also allows for a fast slicing through the cube and assessing the information.
%%
%\com{display of skewed cube, combination of 2D to 3D, navigating between the two views, projection of current slice to the 3D-Cube, details on demand}
%\\\\
\paragraph{2D Mosaic Plot Slice Visualization [4.DD].}
%%
The 2D mosaic visualization (Fig.~\ref{fig:System} c) shows all values below the matrix diagonal of the current slice, creating optical equivalence towards the 3D cube.
%%
To reduce visual clutter, the 2D view only shows dimensions, which are retrieved through the correlation based feature selection.
%%
The free space above the matrix diagonal is used to display the 3D cube.
%%

The purpose of this view is the detailed assessment of the underlying regression models.
%%
By hovering over a data entry in the plot, a tooltip model displays detailed information about a models coefficients, associated $p$ values and confidence intervals.
%%

@@

The statistical processors yield the second structure.
%%
They rely on the statistical programming language \texttt{R}.\footnote{Open Source; \href{http://r-project.org}{\texttt{r-project.org}}}
%%
It is widely adopted in the statistical analysis community, yielding a rich support of fast state-of-the-art statistics algorithms as well newly published methods.
%%
\texttt{OpenCPU} is a \texttt{R} package and provides a API for accessing it via HTTP calls \cite{Ooms}.
%%
This way, any computer, which runs \texttt{R} can be turned into a statistical processor for our project.
%%
The back-end functions necessary for all cube calculations are provided via an \texttt{R} package.
%%
It uses multi-core optimization to use all machine CPUs to speed up the calculation process.
%%
The server workload balances are managed by the front-end code.

@@

\section{Application} \label{application}
%%
\begin{figure*}[htb]
 \centering
 \includegraphics[width=7.0in]{figures/application}
 \caption{
 The analysis of the numerical and dichotomized target feature depicting liver-fat values yields similar results (left).
 %%
 In (a), hotspots for somatometrical features with high correlations were found.
 %%
 High correlations were also found for features depicting \emph{hepatic steatosis} (b).
 %%
 A high correlations between \emph{Interleukin-6}, \emph{hepatic steatosis}, \emph{GGT} and \emph{Lipase} (highlighted using arrows) was found during the analysis using the 2D mosaic plot.
 %%
 \com{Caption Breast Fat Data}
 }
  \label{fig:Application}
\end{figure*}
%%
In this section, we describe how we applied the \emph{Regression Cube} to two epidemiological data sets.
%%
The hepatic steatosis data set was analyzed using data mining algorithms, yielding risk groups, which we now analyze further.
%%
Also, we try to reproduce the prior results from this analysis as proof-of-concept of our method.
%%
The breast fat data set is the foundation for an explorative analysis towards the influencing parameters of the parenchyma tissue of the female breast.
%%

>>>>

%% INTERACTION
Rotating with the cube is restricted to the y-axis, preserving the mental map to position individual features.
%%
The cube is always oriented according to the 2D-representation, allowing for an easy mental combination of the two representations.
%%
Allowing more degrees of freedom was confusing to our users and also did not add value to the visualization.
%%
We provide also a zoom functionality using the mouse wheel input.
%%
%\\\\
\paragraph{Cube Slice Selection [3.ZF].}
%%
In order to \emph{Zoom, Filter and Analyze Further}, the user has to navigate towards different slices of interest.
%%
We propose two ways to achieve this.
\begin{itemize}
	\item \emph{Applying the slicing metaphor from 3D volume data.}
	%%
	In medical volume data renderings, slicing views very common to view details on a selected plane in the scene.
	%%
	We employ this technique for selecting cube slices (e.g. by moving a plane via vertical mouse input while pressing the right mouse button).
	%%
	We, however, still display the whole 3D-object instead of cutting away information towards the slice position.
	%%
	\item \emph{Selecting the slice using a dropdown menu} provides fast access to plane selections when the user already knows the slices of interest.
	%%
\end{itemize}
%%
The currently selected slice is denoted with a semi-transparent gray plane.
%%
The space available from visualizing only the prism generated from the upper half of the cube diagonal is used to display information about the current selected plane.
%%
the values are projected on this plane to give an overlapping-free view on the data points, which makes it easier to identify the current slice.
%%
%It also allows for a fast slicing through the cube and assessing the information.
%%
%\com{display of skewed cube, combination of 2D to 3D, navigating between the two views, projection of current slice to the 3D-Cube, details on demand}
%\\\\
\paragraph{2D Mosaic Plot Slice Visualization [4.DD].}
%%
The 2D mosaic visualization (Fig.~\ref{fig:System} c) shows all values below the matrix diagonal of the current slice, creating optical equivalence towards the 3D cube.
%%
To reduce visual clutter, the 2D view only shows dimensions, which are retrieved through the correlation-based feature selection.
%%
The free space above the matrix diagonal is used to display the 3D cube.
%%

The purpose of this view is the detailed assessment of the underlying regression models.
%%
% TODO: p values kurz nennen? woher kommen die confidence intervals?
By hovering over a data entry in the plot, a tooltip model displays detailed information about a model's coefficients, associated $p$ values and confidence intervals.
%%

@@

The statistical processors yield the second structure.
%%
They rely on the statistical programming language \texttt{R}.\footnote{Open Source; \href{http://r-project.org}{\texttt{r-project.org}}}
%%
It is widely adopted in the statistical analysis community, yielding a rich support of fast state-of-the-art statistics algorithms as well newly published methods.
%%
\texttt{OpenCPU} is an \texttt{R} package and provides an API for accessing it via HTTP calls \cite{Ooms}.
%%
This way, any computer, which runs \texttt{R} can be turned into a statistical processor for our project.
%%
The back-end functions necessary for all cube calculations are provided via an \texttt{R} package.
%%
It uses multi-core optimization to use all machine CPUs to speed up the calculation process.
%%
The server workload balances are managed by the front-end code.

@@

\section{Application} \label{application}
%%
\begin{figure*}[htb]
 \centering
 \includegraphics[width=7.0in]{figures/application}
 \caption{
 The analysis of the numerical and dichotomized target feature depicting liver-fat values yields similar results (left).
 %%
 In (a), hot spots for somatometrical features with high correlations were found.
 %%
 High correlations were also found for features depicting \emph{hepatic steatosis} (b).
 %%
 A high correlation between \emph{Interleukin-6}, \emph{hepatic steatosis}, \emph{GGT} and \emph{Lipase} (highlighted using arrows) was revealed during the analysis using the 2D mosaic plot.
 %%
 \com{Caption Breast Fat Data}
 }
  \label{fig:Application}
\end{figure*}
%%
In this section, we describe how we applied the \emph{Regression Cube} to two epidemiological data sets.
%%
The hepatic steatosis data set was analyzed using data mining algorithms, yielding risk groups, which we now analyze further.
%%
Also, we try to reproduce the prior results from this analysis as proof-of-concept of our method.
%%
The breast fat data set is the foundation for an explorative analysis towards the influencing parameters of the parenchyma tissue of the female breast.
%%
